The \dealii Library, Version 9.1

### 2019-05-12 9.1/paper.tex
do not break author names, add new affiliation
add another grant

\author[2]{Wolfgang Bangerth}
\affil[2]{Department of Mathematics, Colorado State University, Fort
  Collins, CO 80523-1874, USA.
    {\texttt{bangerth@colostate.edu}}}

\author[3]{Denis Davydov}
\affil[3]{Chair of Applied Mechanics,
  Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  Egerlandstr.\ 5,
  91058 Erlangen, Germany.
  {\texttt{\{denis.davydov,jean-paul.pelteret\}@fau.de}}}

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
%
\author[5]{Luca Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}

\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}

\author[4]{Jean-Paul Pelteret}

\author[1]{Bruno Turcksin}

@@

D.~Davydov was supported by the German Research Foundation (DFG), grant DA
1664/2-1.

>>>>

\author[2]{Wolfgang~Bangerth}
\affil[2]{Department of Mathematics, Colorado State University, Fort
  Collins, CO 80523-1874, USA.
    {\texttt{bangerth@colostate.edu}}}

\author[3]{Denis~Davydov}
\affil[3]{Chair of Applied Mechanics,
  Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  Egerlandstr.\ 5,
  91058 Erlangen, Germany.
  {\texttt{\{denis.davydov,jean-paul.pelteret\}@fau.de}}}

\author[4]{Timo~Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
%
\author[5]{Luca~Heltai}
\affil[5]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy.
{\texttt{luca.heltai@sissa.it}}}

\author[6]{Martin~Kronbichler}
\affil[6]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[7]{Matthias~Maier}
\affil[7]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[4]{Jean-Paul~Pelteret}

\author[1]{Bruno~Turcksin}

@@

D.~Davydov was supported by the German Research Foundation (DFG), grant DA
1664/2-1 and the Bayerisches Kompetenznetzwerk
f\"ur Technisch-Wissenschaftliches Hoch- und H\"ochstleistungsrechnen
(KONWIHR).
